Distributional Trees and Forests

### 2017-12-03 pkg/disttree/inst/draft/draft.Rnw
changed ylim of PIT-histograms
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1800 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 7f4575af896e18b07dce31f56c0928d8c12bfe90

par(mfrow = c(2,2))
pithist(pit_df_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Forest", ylim = c(0,1.4))
pithist(pit_g_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "prespecified GAM", ylim = c(0,1.4))
pithist(pit_gb_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "boosted GAM", ylim = c(0,1.4))
pithist(pit_ml_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "EMOS", ylim = c(0,1.4))

>>>>

par(mfrow = c(2,2))
pithist(pit_df_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Forest", ylim = c(0,1.5))
pithist(pit_g_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "prespecified GAM", ylim = c(0,1.5))
pithist(pit_gb_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "boosted GAM", ylim = c(0,1.5))
pithist(pit_ml_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "EMOS", ylim = c(0,1.5))
